The Practical Application of Computerised Multistage Tests

### 2021-03-03 article.Rmd
Added cut score image

```{r Stage 1 MCC}
moduleA1_items <- which(colnames(dfTrial) %in% colnames(dfModuleAItems))
plotData <- trueScoreSummary(plot(raschmodel, 
                                  type = "ICC", 
                                  items = moduleA1_items, plot = FALSE), 
                             "A")
ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
You can read this off such that a candidate who scores 9 in module A would have an estimated ability score, or $\hat{\theta}$, of approximately 1.92.

@@

>>>>

```{r Stage 1 MCC}
moduleA1_items <- which(colnames(dfTrial) %in% colnames(dfModuleAItems))
plotData <- trueScoreSummary(plot(raschmodel, 
                                  type = "ICC", 
                                  items = moduleA1_items, plot = FALSE), 
                             "A")
ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line() +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
You can read this off such that a candidate who scores 9 in module A would have an estimated ability score, or $\hat{\theta}$, of approximately 1.92.

@@

![Cut Score](images/cut-score.png)
